Chord: A Versatile Platform for Program Analysis

### 2011-04-17 main/doc/predefined.tex
more documentation

Each predefined analysis in Chord has a unique name that can be used to run the
analysis from the command-line.  The following command runs the analysis named
\code{<ANALYSIS_NAME>} on the program specified by directory \code{<WORK_DIR>}
(see Chapter \ref{chap:setup} for how to setup a program):

@@

Each analysis in Chord is written modularly, independent of other analyses,
along with lightweight annotations specifying the inputs and outputs of the
analysis.  Chord's runtime automatically computes producer-consumer
relationships between analyses (e.g., determines which analysis produces as
output a result that is needed as input by another analysis).  Before running a
desired analysis (such as 0CFA in the above example), Chord recursively runs
other analyses until the inputs to the desired analysis have been computed; it
finally runs the desired analysis to produce the outputs of that analysis.

The 0CFA analysis consumes and produces multiple {\it program relations}.  The
consumed program relations include \code{MputStatFldInst} and \code{statIM},
each of which is produced by a separate imperative analysis with the
corresponding name, and the produced program relations include \code{VH},
\code{FH}, \code{HFH}, and \code{IM}.  We next briefly discuss these relations.

@@

Metavariables $m$, $f$, $i$, and $v$ above range over entities in so-called
{\it program domains} \code{M}, \code{F}, \code{I}, and \code{V}, respectively.
A program domain is a set of entities of a certain kind in the input Java
program.  For instance, \code{M} is the domain representing the set of all
methods in the input Java program, \code{F} is the domain representing the set
of all fields, \code{I} is the domain representing the set of all call sites in
methods in \code{M}, and \code{V} is the domain representing the set of all
local variables of reference type in methods in \code{M}.  Each of these domains
is produced by a separate Java analysis with the corresponding name.  Notice
that the analyses producing these domains run upfront because these domains are
consumed by the analyses that produce relations such as \code{MputStatFldInst}
and \code{statIM}, which in turn are consumed by the desired 0CFA analysis.

@@

The verbosity of Chord's output above is controlled by property
\code{chord.verbose}, whose default value is 1.  At verbosity level 0, the above
command produces less voluminous output of the form:

@@

To run this analysis, run the following command:

@@

where \code{<WORK_DIR>} is a directory
containing a file named \code{chord.properties} that defines
properties \code{chord.main.class} and \code{chord.class.path} specifying
the main class and the application classpath, respectively, of the program
to be analyzed.

@@

%is implemented in \code{chord/analyses/alias/cipa-0cfa.dlog}.

@@

To run Chord's static datarace analysis, run the following command:

@@

where \code{<WORK_DIR>} is a directory containing a file named
\code{chord.properties} that defines properties \code{chord.main.class},
\code{chord.class.path}, and \code{chord.src.path} specifying the main class,
the application classpath, and the Java source path, respectively, of the
program to be analyzed.

Directory \code{<CHORD_MAIN_DIR>/examples/datarace_test/} provides a toy Java
program on which one can run the datarace analysis.  First run {\tt ant} in that
directory (in order to compile the program's {\tt .java} files to {\tt .class}
files) and then run the above command with \code{<WORK_DIR>} replaced by
\code{examples/datarace_test/}.  Upon successful completion, the following files
should be produced in directory \code{examples/datarace_test/chord_output/}:

@@

To run Chord's static deadlock analysis, run the following command:

@@

where \code{<WORK_DIR>} is a directory containing a file named
\code{chord.properties} that defines properties \code{chord.main.class},
\code{chord.class.path}, and \code{chord.src.path} specifying the main class,
the application classpath, and the Java source path, respectively, of the
program to be analyzed.

Directory \code{<CHORD_MAIN_DIR>/examples/deadlock_test/} provides a toy Java
program on which one can run the deadlock analysis.  First run {\tt ant} in that
directory (in order to compile the program's {\tt .java} files to {\tt .class}
files) and then run the above command with \code{<WORK_DIR>} replaced by
\code{examples/deadlock_test/}.  Upon successful completion, the file
\code{deadlocks.html} should be produced in directory
\code{examples/deadlock_test/chord_output/}.

>>>>

Each analysis in Chord is written modularly, independent of other analyses,
along with lightweight annotations specifying the inputs and outputs of the
analysis.  Chord's runtime automatically computes dependencies between analyses
(e.g., determines which analysis produces as output a result that is needed as
input by another analysis).  Before running a desired analysis, Chord
recursively runs other analyses until the inputs to the desired analysis have
been computed; it finally runs the desired analysis to produce the outputs of
that analysis.

Each analysis in Chord has a unique name that can be used to run the
analysis from the command-line.  You can obtain the names of all analyses
predefined in Chord by running the following command:

\begin{framed}
\begin{verbatim}
ant -Dchord.out.dir=<OUT_DIR> -Dchord.print.project=true run
\end{verbatim}
\end{framed}

This command produces files \code{targets_sortby_name.html}, \code{targets_sortby_kind.html},
and \code{targets_sortby_producers.html} in directory \code{<OUT_DIR>}.  These
files publish the names and descriptions of all analyses that are predefined in
Chord, along with the inputs and outputs of each analysis.

The following command runs the analysis
named \code{<ANALYSIS_NAME>} on the program specified by directory \code{<WORK_DIR>}
(see Chapter \ref{chap:setup} for how to setup a program):

@@

The 0CFA analysis consumes and produces multiple {\it program relations}.  The
consumed program relations include \code{MputStatFldInst} and \code{statIM},
each of which is produced by a separate analysis with the corresponding name.
The produced program relations include \code{VH}, \code{FH}, \code{HFH}, and
\code{IM}.  We next briefly discuss these relations.

@@

Metavariables $m$, $f$, $i$, and $v$ above range over values in so-called
{\it program domains} \code{M}, \code{F}, \code{I}, and \code{V}, respectively.
A program domain is a set of values of a fixed kind in the input Java
program.  For instance, \code{M} is the domain representing the set of all
methods in the input Java program, \code{F} is the domain representing the set
of all fields, \code{I} is the domain representing the set of all call sites in
methods in \code{M}, and \code{V} is the domain representing the set of all
local variables of reference type in methods in \code{M}.  Each of these domains
is produced by a separate analysis with the corresponding name.  Notice
that the analyses producing these domains run upfront because these domains are
consumed by the analyses that produce relations such as \code{MputStatFldInst}
and \code{statIM}, which in turn are consumed by the desired 0CFA analysis.

@@

The verbosity of Chord's output is controlled by property
\code{chord.verbose}, whose default value is 1.  At verbosity level 0, the above
command produces less voluminous output of the form:

@@

The following command can be used to run this analysis on the program specified
by directory \code{<WORK_DIR>} (see Chapter \ref{chap:setup} for how to setup a
program):

@@

@@

@@

The following command can be used to run Chord's static datarace analysis on the
program specified by directory \code{<WORK_DIR>} (see Chapter \ref{chap:setup}
for how to setup a program):

@@

Directory \code{examples/datarace_test/} provides a toy Java program on which to
run the datarace analysis.  First run {\tt ant} in that directory (in order to
compile the program's {\tt .java} files to {\tt .class} files) and then run the
above command with \code{<WORK_DIR>} replaced by \code{examples/datarace_test/}.
Upon successful completion, the following files should be produced in directory
\code{examples/datarace_test/chord_output/}:

@@

The following command can be used to run Chord's static deadlock analysis on the
program specified by directory \code{<WORK_DIR>} (see Chapter \ref{chap:setup}
for how to setup a program):

@@

Directory \code{examples/deadlock_test/} provides a toy Java program on which to
run the deadlock analysis.  First run {\tt ant} in that directory (in order to
compile the program's {\tt .java} files to {\tt .class} files) and then run the
above command with \code{<WORK_DIR>} replaced by \code{examples/deadlock_test/}.
Upon successful completion, the file \code{deadlocks.html} should be produced in
directory \code{examples/deadlock_test/chord_output/}.
